---
title: "workout01-david-choi"
author: "David Choi"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE}
library(dplyr)
library(ggplot2)
```

```{r echo=FALSE}
shots_data <- read.csv(file = "../data/shots-data.csv", stringsAsFactors = FALSE)

#2PT Effective Shooting % by Player
grouped2 <- group_by(filter(shots_data, shots_data$shot_type == "2PT Field Goal"), name)
out_table2 <- summarise(grouped2, total = n(), made = sum(shot_made_flag == "shot_yes"), perc_made = (made/total)) %>% arrange(desc(perc_made))

#3PT Effective Shooting % by Player
grouped3 <- group_by(filter(shots_data, shots_data$shot_type == "3PT Field Goal"), name)
out_table3 <- summarise(grouped3, total = n(), made = sum(shot_made_flag == "shot_yes"), perc_made = (made/total)) %>% arrange(desc(perc_made))

#Effective Shooting % by Player 
grouped <- group_by(shots_data, name)
out_table <- summarise(grouped, total = n(), made = sum(shot_made_flag == "shot_yes"), perc_made = (made/total)) %>% arrange(desc(perc_made))
```

#Report on the shot data of five players from the Golden State Warriors
###Stat 133
###David Choi

##Introduction
When a basketball player makes a shot, the score will be determined based on the distance from the basket to the player. Depending on the player, some players will be more likely to successfully throw the ball into the basket when they throw from close distance, and others will relatively do better from far distance