---
title: "Introduction to Package Binomial"
author: "David Choi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Package Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial

The package '"binomial"' is a implementation for calculating probabilities, creating a data frames, and visualizing the probabilities as the number of successes increase.

## bin_Choose(n, k)
This calculates "n choose k".
```{r}
c <- bin_choose(10, 5)
c
```

## bin_probability(success, trials, prob)
This function calculates the probabilities of getting given number of successes out of given trials where probability of one success is given as well.
```{r}
p <- bin_probability(2, 5, 0.5)
p
```

##bin_distribution(trials, prob)
This creates a data frame of the number of successes(0 to trials) and corresponding probabilities. The returned data frame is a '"bindis"' object. Using plot() we can draw a plot from the bindis object
```{r}
bd <- bin_distribution(5, 0.5)
bd
plot(bd)
```

##bin_cumulative(trials, prob)
This creates a data frame of the number of successes(0 to trials), corresponding probabilities, and cumulative probabilities. The returned data frame is a '"bincum"' object. Using plot() we can draw a plot from the bincum object
```{r}
bc <- bin_cumulative(5, 0.5)
bc
plot(bc)
```

##bin_variable(trials, prob)
This creates a "'binvar'" object with number of trials and probability of getting a success. Using summary() method, we can print out summary of binomial variable object
```{r}
bv <- bin_variable(5, 0.5)
bv
summary(bv)
```

##bin_mean(trials, prob)
This returns the expected value
```{r}
bin_mean(5, 0.5)
```

##bin_variance(trials, prob)
This returns the variance
```{r}
bin_variance(5, 0.5)
```

##bin_mode(trials, prob)
This returns the mode
```{r}
bin_mode(5, 0.5)
```

##bin_skewness(trials, prob)
This returns the skewness
```{r}
bin_skewness(5, 0.5)
```

##bin_kurtosis(trials, prob)
This returns the kurtosis
```{r}
bin_kurtosis(5, 0.5)
```

